Code to generate the figures needed in 'The influence of small reservoirs on

### 2022-07-20 R/Figures_code/paper_figures.Rmd
figure 5 done

```{r figure 5}
setwd("C:/Directory_thesis_codes")

@@

newdf <- df[, 1:ncol(df)-1]
bounds <- find_bounds(newdf, 1, 1, ma = TRUE, 6)
bounds[bounds == Inf | bounds == -Inf] <- 0
df <- df[, c(1, ncol(df))]
df$lowbound <- bounds$low
df$highbound <- bounds$high
df$ma <- ma(df$Banabuiu, 6)
df <- df[14:nrow(df), ]

@@

>>>>

```{r figure 5a}
setwd("C:/Directory_thesis_codes")

@@

newdf <- df[, seq_len(ncol(df)-1)]
bounds <- find_bounds(newdf, 1, 1, ma = TRUE, 6)
bounds[bounds == Inf | bounds == -Inf] <- 0
df <- df[, c(1, ncol(df))]
df$lowbound <- bounds$low
df$highbound <- bounds$high
df$ma <- ma(df$Banabuiu, 6)
df <- df[14:nrow(df), ]

@@

```{r figure 5b}
setwd("C:/Directory_thesis_codes")

sub <- readOGR("./Data/Shapefile/subbasins_cut_geomfix.shp")
SPI_list <- list.load("./Data/Analysis/DCA/SPI_list.RData")
DCA_AR <- list.load("./Data/Analysis/DCA/DCA_AR.RData")

df <- as.data.frame(array(dim = c(length(SPI_list), 3)))
names(df) <- c("SubbasinID", "SPI-1992", "SPI-2012")
df$SubbasinID <- names(SPI_list)

idx1992 <- DCA_AR[["123"]]$date %in% create_date_vector(1992, 1993)
idx2012 <- DCA_AR[["123"]]$date %in% create_date_vector(2012, 2018)
for(name in names(SPI_list)){
  df$`SPI-1992`[df$SubbasinID %in% name] <- mean(SPI_list[[name]][["fitted"]][idx1992], na.rm = T)
  df$`SPI-2012`[df$SubbasinID %in% name] <- mean(SPI_list[[name]][["fitted"]][idx2012], na.rm = T)
}

sub_merge <- merge(sub, df, by = "SubbasinID")

writeOGR(sub_merge, dsn = "./Data/Shapefile/analysis", layer = "subbasin_SPI_all", driver = "ESRI Shapefile")
```
